SPECS-decadal-MOS

### 2017-08-10 SPECS/specs-decade-mos.Rmd
SPECS MOS R-script

## Display the downscaled reanalysis data for assessing link between large and small scales  - in the shape of EOFs
if (downscaledreanalysis) {
  mu.eof <- EOF(mu.eobs)
  plot(mu.eof,colbar=list(pal='t2m',breaks=seq(-0.02,0.02,by=0.001),type='fill',rev=TRUE),new=FALSE)
  figlab('EOBS',ypos=0.999)

@@

  fw.eof <- EOF(fw.eobs)
  plot(fw.eof,colbar=list(pal='t2m',breaks=seq(-0.01,0.015,by=0.001),type='fill',rev=TRUE),new=FALSE)
  figlab('EOBS',ypos=0.999)

@@

for (iexp in 1:1) {
  print(paste('Get the decadal predictors saved locally in',experiments[iexp]))
  load(experiments[iexp])
  dir <- substr(experiments[iexp],1,nchar(experiments[iexp])-4)
  if (!file.exists(dir)) dir.create(dir)

>>>>

## Display the downscaled reanalysis data for assessing link between large and small scales  - in the shape of EOFs
if (downscaledreanalysis) {
  mu.eof <- EOF(mu.eobs)
  index(mu.eof) <- year(mu.eof)
  plot(mu.eof,colbar=list(pal='t2m',breaks=seq(-0.02,0.02,by=0.001),type='fill',rev=TRUE),new=FALSE)
  figlab('EOBS',ypos=0.999)

@@

  fw.eof <- EOF(fw.eobs)
  index(fw.eof) <- year(fw.eof)
  plot(fw.eof,colbar=list(pal='t2m',breaks=seq(-0.01,0.015,by=0.001),type='fill',rev=TRUE),new=FALSE)
  figlab('EOBS',ypos=0.999)

@@

for (iexp in 1:4) {
  print(paste('Get the decadal predictors saved locally in',experiments[iexp]))
  load(experiments[iexp])
  dir <- substr(experiments[iexp],1,nchar(experiments[iexp])-4)
  if (!file.exists(dir)) dir.create(dir)
